---
title: "2019.Uvic_hagfish_datamanipulation"
author: "Lucas Agagnier"
date: "August 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(xlsx)# reading from excel docs

knitr::opts_chunk$set(echo = TRUE)

fl_in<-"Timmer_2019_JuanesLab-Hagfish_Isotope_data.xlsx"
path<-"C:\\Users\\lagag\\Documents\\00-documents\\2019.juaneshagfish\\hagfish"
t_in<-"all_trays.csv"
setwd(path)

```

#Introduction  
  The best way to extract the data will be from the excel sheets directly and making some text file documents to seperate come tables that have been combined.  
```{r}
t_read<-read.delim(t_in,sep = ",")
head(t_read)
```

#Possible need for duplication
  We need to check if the variation is acceptable. There were also some questionable results in tray four. Ive added a row in in the csv file to label which runs were questionable called "ques". I will exclude those from the intial box plots and check them against it.  
```{r}
t_solid_alltrays<-t_read[!t_read$ques==TRUE,]#definate values
t_ques_tray4<-t_read[t_read$ques==TRUE,]#values that had problems

head(t_solid_alltrays)

head(t_ques_tray4)

boxplot(t_solid_alltrays$C.N)#this is too general and we need to break things down before we can say anything for sure

```
##muscles  

```{r}
mscl<-t_solid_alltrays[t_solid_alltrays$sample.type=="muscle",]
head(mscl)
boxplot(mscl$C.N)
```
##loop for all sample types  
```{r}
unvec<-unique(t_solid_alltrays$sample.type)

t_ques_tray4<-t_ques_tray4[rowSums(is.na(t_ques_tray4))==0,]

  samp_tiss<-t_solid_alltrays[t_solid_alltrays$sample.type=="muscle",]
  qu_samptiss<-t_ques_tray4[t_ques_tray4$sample.type=="muscle",]
  
  x<-ggplot(data = samp_tiss,aes(x=samp_tiss$sample.type,y=samp_tiss$C.N))+geom_boxplot(colour="blue")#+geom_bar(data=qu_samptiss,aes(x=qu_samptiss$sample.type,y=qu_samptiss$C.N))
  
  samp_tiss_1<-t_solid_alltrays[t_solid_alltrays$sample.type=="liver",]
  y<-ggplot(data = samp_tiss_1,aes(x=samp_tiss_1$sample.type,y=samp_tiss_1$C.N))+geom_boxplot()
  samp_tiss_2<-t_solid_alltrays[t_solid_alltrays$sample.type=="standard",]
  z<-ggplot(data = samp_tiss_2,aes(x=samp_tiss_2$sample.type,y=samp_tiss_2$C.N))+geom_boxplot()
  x
  y
  z
```

```{r}
filter(t_read,t_read$sample.type=="muscle"&&t_read$ques==FALSE)
ggplot(data = t_read,aes(x=t_read$sample.type,y=t_read$C.N))+geom_boxplot()+geom_point(data = t_read,aes(x))
```


  
  